### 2018-06-13 manuscript.tex
Update manuscript.tex

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+ \cite{Shel-Wand11}

>>>>

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+ \cite{Shel-Wand11}:  Mackie's social convetional theory was supported in their findings; futher, they proposed that fgc practice is beyond the belief of marriage advanges; it goes beyond.  FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriges was not men's refusal of non-fgc women, but hostality and discrimination from fgc women to non fgc women.
